Design and Implementation of a Multithreaded Virtual Machine for Executing Linear Logic Programs

### 2014-09-15 paper.tex
fix

We think that our virtual machine is an excellent starting point to make
logic programming more desirable in the data-mining, machine learning and
distributed/parallel programming community. Moreover, our virtual machine can
be easily extended to execute over computer networks or to execute programs on really big datasets.
In a nutshell, LM provides a concise way to describe
graph-based algorithms that can be more easily reasoned about, a clear advantage over
competing systems.

>>>>

We think that our virtual machine is a promising starting point to make
logic programming more desirable in the data-mining, machine learning and
distributed/parallel programming community. Moreover, our virtual machine can
be easily extended to execute over computer networks or to execute programs on really big datasets.
In a nutshell, LM provides a concise way to describe
graph-based algorithms that can be more easily reasoned about, a clear advantage over
competing systems.
